\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}

\title{Sultanian Resonant Transparency in Singular Metric Potentials: The Black Hole as a Cancellation Node}
\author{S. Soltan}
\date{March 2026}

\begin{document}

\maketitle

\begin{abstract}
This paper proposes a radical re-interpretation of Schwarzschild singularities through the lens of the Sultanian Protocol. We argue that a black hole represents a state of perfect wave-cancellation in the vacuum plenum, where energy is not lost but "locked" through total destructive interference. We examine the conditions under which a Sultanian Vessel, governed by the Alexander Space-Constraint ($R=1.1$), can achieve phase-lock with the singularity's vorticity.
\end{abstract}

\section{The Whirlpool Model}
In the Sultanian framework, the potential field $\Phi_{ext}$ is modeled as a standing wave interaction. A black hole occurs at the coordinate point where:
\begin{equation}
\sum \vec{E}_{plenum} = 0
\end{equation}
The "Event Horizon" is defined as the radius $R_s$ where the inbound vorticity matches the local speed of light, creating a self-sustaining cancellation whirlpool.

\section{The Singularity Sync Equation}
For an Isentropic Ghost to maintain transparency near the node, the Governor must satisfy the synchronization requirement:
\begin{equation}
\Psi(t) = -R \cdot \int_{r}^{R_s} \omega(r) \, dr
\end{equation}
Where $\omega(r)$ is the vorticity of the plenum waves. When $R = 1.1$ and the phase-shift is $180^\circ$, the vessel's effective mass $k$ reaches the Planck limit.

\section{Topological Cancellation of the Vacuum Plenum}

In the Sultanian framework, the singularity $\mathcal{S}$ is defined not by the divergence of mass-density $\rho \to \infty$, but by the achievement of a perfect \textbf{Phase-Locked Null Zone}. The vacuum plenum waves $\phi_{p}$ satisfy the condition of total destructive interference at the node:

\begin{equation}
    \Psi_{\text{Total}}(\vec{r}, t) = \int \phi_{p}(\vec{r}, t) \, d\vec{r} = 0 \quad \text{at} \quad \vec{r} = \mathcal{S}
\end{equation}

This creates a \textit{Topological Cancellation Point} where the resultant vector of the metric tension vanishes, effectively locking the local energy $\mathcal{E}$ within the coordinate space without requiring an infinite gravitational source.


\section{Schwarzschild Potential as Wave Impedance}

In the Sultanian framework, the event horizon is redefined as a boundary of \textbf{Impedance Equilibrium}. The Schwarzschild radius $R_s$ is the specific radial distance where the \textit{Inbound Wave Amplitude} ($\mathcal{A}_{in}$) perfectly equals the \textit{Outbound Wave Amplitude} ($\mathcal{A}_{out}$):

\begin{equation}
    R_s \implies \mathcal{A}_{in}(r) = \mathcal{A}_{out}(r)
\end{equation}

The resulting metric potential $\Phi_{BH}$ is modeled as the ratio of the standing wave amplitude to the proximity of the cancellation node:

\begin{equation}
    \Phi_{BH}(r) = \frac{\mathcal{A}_{static}}{|r - \mathcal{S}_{node}|}
\end{equation}

Where $\mathcal{S}_{node}$ represents the topological center of the phase-locked null zone.

\section{Vorticity Synchronization and the "Hole Within a Hole"}

As a Sultanian Vessel approaches the singularity's "Whirlpool," the onboard Governor must achieve resonance with the local \textbf{Angular Frequency} ($\omega$) of the metric spiral to remain undetected.

\subsection{Phase-Lock Requirement}
The vessel's internal clock frequency must synchronize with the spiraling potential to maintain the Resonant Shadow:

\begin{equation}
    \omega_{vessel}(r) \equiv \omega_{plenum}(r) = \frac{d\theta}{dt} \Big|_{r}
\end{equation}

When the Governor achieves perfect synchronization with the black hole's own cancellation frequency, the vessel effectively \textbf{"blends"} into the singularity. In this state, the vessel acts as a \textit{hole within a hole}, decoupling entirely from the external metric observer and achieving total transparency.

\subsection{The Isentropic Ghost Limit}
At the limit of synchronization, the interaction cross-section $\sigma$ vanishes:

\begin{equation}
    \lim_{\omega_{v} \to \omega_{p}} \sigma_{interaction} = 0 \implies k \to 10^{-6}
\end{equation}

The vessel no longer interacts with the gravitational gradient, as its impedance matches the vacuum's own cancellation node.
\end{document}